Democratizing Secure Two-Party Computation

### 2017-10-13 OaklandSubmission/intro.tex
intro small changes

Suppose a developer wants to compute $w^Tx >0$ securely using SMC. With the current techniques, he has two options. \nc{The two options appear quite far apart in the text. Can we make bullet points maybe?} \divya{Bullet list would look bad. I tried listing both options first and then discussing but its hard to talk about ABY before.} He can code up the functionality in a programmer friendly domain-specific language such as \cite{lambdaps,wysteria,oblivm} that would automatically compile it to an SMC protocol. The downside is that all of these works build on a cryptographic back-end that is either entirely boolean \cite{yao,gmw} or entirely arithmetic \cite{homo}. The efficiency of the generated SMC protocol is hence, bounded by the possibility of efficiently representing the function in a form that is compatible with the cryptographic back-end used. For instance, over $\ell$-bit integers, multiplication requires a boolean circuit of size  $O(\ell^2)$. 
For better efficiency, we would like to evaluate $w^Tx$ using an Arithmetic circuit and the comparison using a boolean circuit.
In fact, most interesting functions require a mix of arithmetic and boolean computations.
To address this issue, recently Demmler et al. \cite{aby} gave a cryptographic protocol for SMC where the parties can mix arithmetic and boolean computations. \footnote{Need to note somewhere that many works combined HE and Yao. Look at ABY for references.}
Hence, the second option is to write the functionality in the system developed in \cite{aby}.
However, using their system requires the programmer to be aware of complex trade-offs between arithmetic and boolean cryptographic schemes. In their framework, the programmer is required to write circuits consisting of  arithmetic and boolean gates along with appropriate conversion gates. In short, as is also mentioned by the authors themselves, the current system is not suitable to be used by non-specialist programmers. \nc{Also say that the programmer would need to know which functionality is better suited for arithmetic/boolean and also how to split the complete functionality into such parts.} \divya{Change tone...}
Our work .....
\nc{Should we also say here that a third option is to hire a cryptographer and build specific crypto protocols for the functionalities? :) This seems to be the option we are targeting when we show our comparisons and we say that we beat or match hand-crafted protocols} \divya{We can do this! wMight have to see the flow.}

>>>>

Suppose a developer wants to compute $w^Tx >0$ securely using SMC. With the current techniques, he has two options. \nc{The two options appear quite far apart in the text. Can we make bullet points maybe?} \divya{Bullet list would look bad. I tried listing both options first and then discussing but its hard to talk about ABY before.} He can code up the functionality in a programmer friendly domain-specific language such as \cite{lambdaps,wysteria,oblivm} that would automatically compile it to an SMC protocol. The downside is that all of these works build on a cryptographic back-end that is either entirely boolean \cite{yao,gmw} or entirely arithmetic \cite{homo}. The efficiency of the generated SMC protocol is hence, bounded by the possibility of efficiently representing the function in a form that is compatible with the cryptographic back-end used. For instance, over $\ell$-bit integers, multiplication requires a boolean circuit of size  $O(\ell^2)$. 
For better efficiency, we would like to evaluate $w^Tx$ using an Arithmetic circuit and the comparison using a boolean circuit.
In fact, most interesting functions require a mix of arithmetic and boolean computations.
To address this issue, recently Demmler et al. \cite{aby} gave a cryptographic protocol for SMC where the parties can mix arithmetic and boolean computations. \footnote{Need to note somewhere that many works combined HE and Yao. Look at ABY for references.}
Hence, the second option is to write the functionality in the system developed in \cite{aby}.
However, using their system requires the programmer to be aware of complex trade-offs between arithmetic and boolean cryptographic schemes and split the functionality into such parts accordingly. In their framework, the programmer is required to write circuits consisting of  arithmetic and boolean gates along with appropriate conversion gates. In short, the current system of ABY is not suitable to be used by non-specialist programmers. 
\nc{Also say that the programmer would need to know which functionality is better suited for arithmetic/boolean and also how to split the complete functionality into such parts.}
Now the third option is to hire a cryptographer to design specialised protocols for the functionalities. 
In our work, we achieve the best of all options. \divya{add a word like automatically..}
\nc{Should we also say here that a third option is to hire a cryptographer and build specific crypto protocols for the functionalities? :) This seems to be the option we are targeting when we show our comparisons and we say that we beat or match hand-crafted protocols} \divya{We can do this! Might have to see the flow.}
